\bf Fast, Scalable Phrase-Based SMT Decoding

### 2016-06-10 acl.2016/amta2016.tex
whatever

The search algorithm creates and destroy a large number of intermediate objects such as hypotheses and feature function states. The memory management this requires puts a burden on the operating system due to the need to synchronize memory access. This problem worsens with multi-threaded applications such as Moses.

Libraries such as tcmalloc~\citep{ghemawat2009tcmalloc} are designed to reduce locking contention for multi-threaded application but in our case, this is still not enough.

@@

A memory pool is a large block of memory that has been given to the application by the operating system. The application is then responsible for allocating portions of this memory to its components as required. We will use thread-specific memory pools to increase speed by avoiding locking contention during memory access. Our memory pools will be dynamic, growing in size when required but never reducing in size. The pools are not deleted until the decoder application ends.

To further increase memory management speed, objects in the memory pool are not deleted. Unused data structures accumulates in the pool until a reset event. After the event, the pool is assumed to be empty and simply reused.

We instantiate two memory pools per decoding thread, one which is never reset and another which is reset after the decoding of each sentence. Data structures are created in either pool according to their life cycle.

>>>>

The search algorithm creates and destroy a large number of intermediate objects such as hypotheses and feature function states. This puts a burden on the operating system due to the need to synchronize memory access, especially when using a large number of threads. Libraries such as tcmalloc~\citep{ghemawat2009tcmalloc} are designed to reduce locking contention for multi-threaded application but in our case, this is still not enough.

@@

A memory pool is a large block of memory that has been given to the application by the operating system. The application is then responsible for allocating portions of this memory to its components when requested. We will use thread-specific memory pools to increase speed by avoiding locking contention during memory access. Our memory pools will be dynamic. That is, the memory requirement does not have to be known or specified before running the application, the pool can grow when required but they will never reduce in size. The pools are deleted only when the application ends.

To further increase memory management speed, objects in the memory pool are not deleted. Unused data structures accumulates in the pool until a reset event. The pool is assumed to be empty and simply reused after the event. We instantiate two memory pools per decoding thread, one which is never reset and another which is reset after the decoding of each sentence. Data structures are created in either pool according to their life cycle.
